---
title: "Tutorial: Full dashboard UI in Shiny and Fluent"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial: Full dashboard in Fluent UI}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shiny.fluent)
```

```{r, include=FALSE, cache=FALSE}
do.call(knitr::read_chunk, list(path = "../inst/examples/tutorial/dashboard_layout.R"))
```

This is Part 2 of shiny.fluent tutorial.

In [Part 1](../articles/shiny-fluent.html) we built a pretty functional app, but it doesn't look great. Let's now build a dashboard UI for that app. It will have a top command bar with a title, a sidebar with navigation, and nicely arranged cards on the analysis page.

# Prerequisites

Let's start by loading all libraries that we will use in this example

```{r libraries, eval=FALSE}
```

# Styling the page

# Dashboard Layout

# Router

# Navbar


*TODO - at least a basic, short version that can be improved*